Summary Tables

### 2023-05-12 summary_tables.Rmd
Update scenario name

for (city in cities) { # Loop for each city
  df <- io[[city]]$trip_scen_sets
  u_trips <- df %>% dplyr::filter(scenario == "Baseline") %>% 
    summarise(uid = n_distinct(trip_id)) %>% as.numeric()
  td <- df %>% distinct(trip_id, scenario, .keep_all = T) %>% 
    group_by(trip_mode, scenario) %>% 
    summarise(p = round(dplyr::n() / u_trips * 100, 1)) %>% 
    spread(key = trip_mode, value = p) %>% 
    mutate(row_sums = rowSums(.[sapply(., is.numeric)], na.rm = TRUE))
  td <- as.data.frame(t(td))
  names(td) <- lapply(append('BASELINE', rownames(scen_prop)), as.character)
  td <- td[-1, ]
  x <- match(row.names(td), trip_order$mode)
  x[!is.na(x)]
  td <- td[order(x),]

>>>>

for (city in cities) { # Loop for each city
  df <- io[[city]]$trip_scen_sets
  u_trips <- df %>% dplyr::filter(scenario == "baseline") %>% 
    summarise(uid = n_distinct(trip_id)) %>% as.numeric()
  td <- df %>% distinct(trip_id, scenario, .keep_all = T) %>% 
    group_by(trip_mode, scenario) %>% 
    summarise(p = round(dplyr::n() / u_trips * 100, 1)) %>% 
    spread(key = trip_mode, value = p) %>% 
    mutate(row_sums = rowSums(.[sapply(., is.numeric)], na.rm = TRUE))
  td <- as.data.frame(t(td))
  names(td) <- lapply(append('BASELINE', rownames(scen_prop)), as.character)
  td <- td[-1, ]
  x <- match(row.names(td), trip_order$mode)
  x[!is.na(x)]
  td <- td[order(x),]
